---
title: "Untitled"
author: "RN7"
date: "4/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse, scales, janitor, gt, rvest, polite, glue, webshot)
```




```{r, eval=FALSE}
tidy_anime <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-04-23/tidy_anime.csv")
```

```{r}
tidy_anime <- readRDS("tidy_anime.RDS")

glimpse(tidy_anime)
```

TV Shows ONLY and Movies ONLY

TITLE:
PICTURE: ![]()
RANK
POPULARITY
Producer: TV emoji icon

:Airing:
FROM TO
(date_format)

Genre: emoji icon
Genre average & + / - comparison
Score: bold + icon    COLOR FILL
Favorites >>> Star Icon or emoji?

Synopsis >> link pop-out?

Footnotes: ??? * if Anime original? Note if sequel?


Chronological look at GUNDAM, Ghibli, Monogatari Series??


```{r}
tidy_anime %>% 
  select(title_english, genre, rank, popularity, score, studio, start_date, end_date, synopsis)
```

```{r}
gundam_raw <- tidy_anime %>% 
  select(-related, -background, -premiered, -related, -members, -airing, -favorites,
         -title_synonyms, -title_japanese, -producers, -status, -broadcast, -genre, -source, -rank, -popularity) %>% 
  ## group by title and slice only top... otherwise 4593745 duplicate rows for each genre...
  group_by(title_english) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ## filter for Gundam in title, filter for TV, OVA, Movie
  filter( str_detect(title_english, "Gundam"), type %in% c("TV", "OVA", "Movie")) %>% 
  ## filter out non-main story stuff and random shorts
  filter(!title_english %in% c("Mobile Suit Gundam SEED MSV Astray",
                               "Mobile Suit Gundam 0083: The Afterglow Of Zeon",
                               "Mobile Suit Gundam SEED Destiny Final Plus: The Chosen Future",
                               "Mobile Suit Gundam Unicorn Perfectibility",
                               "Mobile Suit Gundam Unicorn RE:0096",
                               "Mobile Suit Gundam Wing: Operation Meteor",
                               "Mobile Suit SD Gundam's Counterattack",
                               "Mobile Suit SD Gundam Festival",
                               "Musha, Knight, Commando: SD Gundam Emergency Sortie",
                               "Mobile Suit Zeta Gundam: A New Translation - Heir to the Stars",
                               "Mobile Suit Zeta Gundam: A New Translation II - Lovers",
                               "Mobile Suit Zeta Gundam: A New Translation III - Love Is the Pulse of the Stars",
                               "Mobile Suit Gundam 00 Special Edition",
                               "∀ Gundam I: Earth Light",
                               "∀ Gundam II: Moonlight Butterfly")) %>% 
  select(-duration, -scored_by, -synopsis) %>% 
  ## chronological order
  arrange(start_date)
```

```{r}
gundam_df <- gundam_raw %>% 
  ## calculate mean score for entire-ish franchise
  ## fill in end dates, for movies just fill with start_date
  mutate(avg_score = mean(score) %>% round(digits = 2),
         end_date = case_when(
           title_english == "Gundam Build Fighters Try" ~ as.Date("2015-04-01"),
           title_english == "Mobile Suit Gundam: Iron-Blooded Orphans 2nd Season" ~ as.Date("2017-04-02"),
           title_english == "Mobile Suit Gundam Unicorn" ~ as.Date("2014-06-06"),
           title_english == "Mobile Suit Gundam: The Origin" ~ as.Date("2018-05-05"),
           type == "Movie" ~ start_date,
           TRUE ~ end_date
         ),
         title_english = case_when(
           lubridate::year(end_date) == 2000 ~ "Turn A Gundam",
           TRUE ~ title_english
         )) %>% 
  ## create "decade" groupings for gt subheaders
  ## create html link to MAL webpage
  mutate(newscore = score - avg_score, 
         end_year = lubridate::year(end_date),
         decade = case_when(
           end_year %in% c(1980:1989) ~ "1980's",
           end_year %in% c(1990:1999) ~ "1990's",
           end_year %in% c(2000:2009) ~ "2000's",
           end_year %in% c(2010:2019) ~ "2010's"),
         rating = str_replace(rating, " -.*", ""),
         link = map(animeID, ~paste0("https://myanimelist.net/anime/", .x)) %>% unlist,
         link = glue("[MAL Link]({link})"),
         link = md(link)) %>% 
  arrange(desc(score)) %>% 
  mutate(score_rank = row_number()) %>% 
  arrange(start_date)
```


## MAL pic

```{r}
# https://myanimelist.net/anime/2581

mal_


gundam_df %>% 
  mutate(link = map(animeID, ~paste0("https://myanimelist.net/anime/", .x)) %>% unlist,
         link = glue("[MAL Link]({link})"))
```




```{r}
gundam_gt <- gundam_df %>% 
  group_by(decade) %>% 
  gt() %>% 
  tab_header(title = "Mobile Suit Gundam", 
             subtitle = md("All major stories in Universal Century and alternate universes")) %>% 
  cols_label(
    "title_english" = "Title",
    "episodes" = "# of Episodes",
    "studio" = "Studio",
    "start_date" = "From",
    "end_date" = "To",
    "rating" = "Rating",
    "score" = "Score",
    "type" = "Type",
    "score_rank" = "Rank",
    "link" = "Link") %>% 
  cols_align(align = "center") %>% 
  tab_spanner(
    label = "Airing Dates",
    columns = vars("start_date", "end_date")
  ) %>% 
  tab_style(
      style = cells_styles(
        text_color = "green",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore >= 0.5 & newscore < 1
      ))
    ) %>% 
  tab_style(
      style = cells_styles(
        text_color = "#49f149",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore >= 0 & newscore < 0.5
      ))
    ) %>% 
  tab_style(
      style = cells_styles(
        text_color = "orange",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore >= -0.5 & newscore < 0
      ))
    ) %>% 
  tab_style(
      style = cells_styles(
        text_color = "red",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore >= -1 & newscore < -0.5
      ))
    ) %>% 
  tab_style(
      style = cells_styles(
        text_color = "purple",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore < -1
      ))
    ) %>% 
  fmt_date(columns = vars(start_date, end_date),
           date_style = 5) %>% 
  cols_hide(columns = vars(newscore, avg_score, end_year, studio, animeID)) %>% 
  tab_style(style = cells_styles(
    text_size = 20,
    text_font = "Roboto Condensed",
    text_color = "white",
    text_decorate = "underline",
    bkgd_color = "blue"),
    locations = list(cells_group("1980's"),
                     cells_group("1990's"),
                     cells_group("2000's"),
                     cells_group("2010's"))) %>% 
  tab_options(heading.background.color = "red",
              heading.title.font.size = 26,
              heading.subtitle.font.size = 22) %>% 
  tab_style(
    style = cells_styles(text_font = "Roboto Condensed"),
    locations = list(cells_title(groups = "title"))
  ) %>% 
  tab_style(
    style = cells_styles(text_weight = "bolder"),
    locations = cells_data(columns = "title_english")
  ) %>% 
  tab_footnote(
    footnote = "Ranked by Score",
    locations = cells_column_labels(columns = "score_rank")
  ) %>% 
  tab_footnote(
    footnote = "Color-coded based on average rating: 7.61",
    locations = cells_column_labels(columns = "score")
  ) %>% 
  fmt_markdown(columns = vars("link")) %>% 
  cols_move_to_end(columns = vars("link")) %>% 
  tab_source_note(source_note = "Source: MyAnimeList, #TidyTuesday by @R_by_Ryo") 
```




```{r, fig.width=10}
gundam_df %>% 
  group_by(decade) %>% 
  gt() %>% 
  ## title style
  tab_header(title = "Mobile Suit Gundam", 
             subtitle = md("All major stories in Universal Century and alternate universes")) %>% 
  tab_options(heading.background.color = "red",
              heading.title.font.size = 26,
              heading.subtitle.font.size = 22) %>% 
  tab_style(
    style = cells_styles(text_font = "Roboto Condensed"),
    locations = list(cells_title(groups = "title"))
  ) %>% 
  ## change label names
  cols_label(
    "title_english" = "Title",
    "episodes" = "# of Episodes",
    "studio" = "Studio",
    "start_date" = "From",
    "end_date" = "To",
    "rating" = "Rating",
    "score" = "Score",
    "type" = "Type",
    "score_rank" = "Rank",
    "link" = "Link") %>% 
  ## spanner title
  tab_spanner(
    label = "Airing Dates",
    columns = vars("start_date", "end_date")
  ) %>% 
  ## Color-fill scores
  tab_style(
      style = cells_styles(
        text_color = "green",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore >= 0.5 & newscore < 1
      ))
    ) %>% 
  tab_style(
      style = cells_styles(
        text_color = "#49f149",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore >= 0 & newscore < 0.5
      ))
    ) %>% 
  tab_style(
      style = cells_styles(
        text_color = "orange",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore >= -0.5 & newscore < 0
      ))
    ) %>% 
  tab_style(
      style = cells_styles(
        text_color = "red",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore >= -1 & newscore < -0.5
      ))
    ) %>% 
  tab_style(
      style = cells_styles(
        text_color = "purple",
        text_weight = "bold"
      ),
      locations = list(cells_data(
        columns = vars(score),
        rows = newscore < -1
      ))
    ) %>% 
  ## Group title style
  tab_style(style = cells_styles(
    text_size = 20,
    text_font = "Roboto Condensed",
    text_color = "white",
    text_decorate = "underline",
    bkgd_color = "blue"),
    locations = list(cells_group("1980's"),
                     cells_group("1990's"),
                     cells_group("2000's"),
                     cells_group("2010's"))) %>% 
  ## Show title
  tab_style(
    style = cells_styles(text_weight = "bolder"),
    locations = cells_data(columns = "title_english")
  ) %>% 
  ## Footnotes
  tab_footnote(
    footnote = "Ranked by Score",
    locations = cells_column_labels(columns = "score_rank")
  ) %>% 
  tab_footnote(
    footnote = "Color-coded based on average rating: 7.61",
    locations = cells_column_labels(columns = "score")
  ) %>% 
  ## Misc.
  cols_align(align = "center") %>% 
  fmt_date(columns = vars(start_date, end_date),
           date_style = 5) %>% 
  cols_hide(columns = vars(newscore, avg_score, end_year, studio, animeID)) %>% 
  fmt_markdown(columns = vars("link")) %>% 
  cols_move_to_end(columns = vars("link")) %>% 
  tab_source_note(source_note = "Source: MyAnimeList, #TidyTuesday by @R_by_Ryo")
```


```{r}
gtsave <- function(data,
                   filename,
                   ...) {

  # Input object validation
  #stop_if_not_gt(data)

  # Get the lowercased file extension
  file_ext <- gtsave_file_ext(filename)

  # Stop function if a file extension is not provided
  if (file_ext == "") {

    stop("A file extension is required in the provided filename. We can use:\n",
         " * `.html`/`.htm` (HTML file)\n",
         " * `.tex`/`.ltx`/`.rnw` (LaTeX file)\n",
         " * `.rtf` (RTF file)\n",
         " * `.png` (PNG file)\n",
         " * `.jpg/.jpeg` (JPEG file)\n",
         " * `.pdf` (PDF file)",
         call. = FALSE)
  }

  # Use the appropriate save function based
  # on the filename extension
  switch(file_ext,
          htm = gt_save_html(data, filename, ...),
         html = gt_save_html(data, filename, ...),
          ltx = gt_save_latex(data, filename, ...),
          rnw = gt_save_latex(data, filename, ...),
          tex = gt_save_latex(data, filename, ...),
          rtf = gt_save_rtf(data, filename, ...),
          png = gt_save_webshot(data, filename, ...),
          pdf = gt_save_webshot(data, filename, ...),
         {
           stop("The file extension used (`.", file_ext, "`) doesn't have an ",
                "associated saving function.\n",
                " * We can use either of `.html`/`.htm`, `.tex`/`.ltx`/`.rnw`, or `.rtf`",
                call. = FALSE)
         }
  )
}

#' Saving function for an HTML file
#'
#' @importFrom htmltools as.tags save_html HTML
#' @noRd
gt_save_html <- function(data,
                         filename,
                         ...,
                         inline_css = FALSE) {

  if (inline_css) {

    data %>%
      as_raw_html(inline_css = inline_css) %>%
      htmltools::HTML() %>%
      htmltools::save_html(filename)

  } else {

    data %>%
      htmltools::as.tags() %>%
      htmltools::save_html(filename)
  }
}

#' Saving function for an image file via the webshot package
#'
#' @noRd
gt_save_webshot <- function(data,
                            filename,
                            ...,
                            zoom = 2,
                            expand = 5) {

  # Create a temporary file with the `html` extension
  tempfile_ <- tempfile(fileext = ".html")

  # Reverse slashes on Windows filesystems
  tempfile_ <-
    tempfile_ %>%
    tidy_gsub("\\\\", "/")

  # Save gt table as HTML using the `gt_save_html()` function
  gundam_gt %>% gt_save_html(filename = tempfile_)

  # Saving an image requires the webshot package; if it's
  # not present, stop with a message
  if (requireNamespace("webshot", quietly = TRUE)) {

    # Save the image in the working directory
    webshot::webshot(
      url = "gundam_gt.html",
      file = "gundam_gt.png",
      selector = "table",
      zoom = 2,
      expand = 5
    )

  } else {
    stop("The `webshot` package is required for saving images of gt tables.",
         call. = FALSE)
  }
}


gtsave_file_ext <- function(filename) {

  tools::file_ext(filename) %>% tolower()
}

tidy_gsub <- function(x, pattern, replacement, fixed = FALSE) {

  gsub(pattern, replacement, x, fixed = fixed)
}
```




```{r}
gt_save_html <- function(data,
                         filename,
                         ...,
                         inline_css = FALSE) {
  
  if (inline_css) {
  }}



gt_save_webshot <- function(data,
                            filename,
                            ...,
                            zoom = 2,
                            expand = 5) {
  
  # Create a temporary file with the `html` extension
  tempfile_ <- tempfile(fileext = ".html")
  
  # Reverse slashes on Windows filesystems
  tempfile_ <-
    tempfile_ %>%
    tidy_gsub("\\\\", "/")
  
  # Save gt table as HTML using the `gt_save_html()` function
  data %>% gt_save_html(filename = tempfile_)
  
  # Saving an image requires the webshot package; if it's
  # not present, stop with a message
  if (requireNamespace("webshot", quietly = TRUE)) {
    
    # Save the image in the working directory
    webshot::webshot(
      url = paste0("file:///", tempfile_),
      file = filename,
      selector = "table",
      zoom = zoom,
      expand = expand
    )
    
  } else {
    stop("The `webshot` package is required for saving images of gt tables.",
         call. = FALSE)
  }
}

## gtsave PNG
gtsave_png <- function(data,
                       filename,
                       ...) {
  
  
  if (file_ext == "") {
    stop("A file extension is required in the provided filename. We can use:\n",
         " * `.html`/`.htm` (HTML file)\n",
         " * `.tex`/`.ltx`/`.rnw` (LaTeX file)\n",
         " * `.rtf` (RTF file)\n",
         " * `.png` (PNG file)\n",
         " * `.jpg/.jpeg` (JPEG file)\n",
         " * `.pdf` (PDF file)",
         call. = FALSE)
  }
  
  switch(file_ext,
         png = gt_save_webshot(data, filename, ...),
         {
           stop("The file extension used (`.", file_ext, "`) doesn't have an ",
                "associated saving function.\n",
           )
         })
}

gtsave_png(filename = "gundam_gt.png")
         
```

















- footnotes: score >>> fill scale dependent on + / - avg score
-- -2 -1 /  -1 -0.5 / -0.5 0 +0.5 / +0.5 +1 / +1 +2
- studio as a sub-header separate
- color fill on rating
- airing and from-to subheader

```{r}
gundam_df %>% 
  #group_by(decade) %>% 
  gt(groupname_col = "decade",
     rownames_to_stub = TRUE,
     rowname_col = "title_english") %>% 
  #tab_header(title = "Mobile Suit Gundam") %>% 
  summary_rows(
    groups = FALSE,
    columns = vars(score, favorites),
    fns = list(thingymacdoodle = ~sum(.)))
```




```{r}
gundam_synopsis <- tidy_anime %>% 
  select(-related, -animeID, -name, -background, -premiered, -related, -members, -episodes, -airing, 
         -title_synonyms, -title_japanese, -producers, -status, -broadcast, -genre, -source, -rank, -popularity) %>% 
  group_by(title_english) %>% 
  slice(1) %>% 
  ungroup() %>% 
  filter(str_detect(title_english, "Gundam"), type == "TV") %>% 
  select(title_english, synopsis) 
```




```{r}
tidy_anime %>% 
  summarize(avg_num_scorers = mean(scored_by))

tidy_anime %>% 
  select(genre) %>% 
  unique()
```




```{r}
tidy_anime %>% 
  select(-genre) %>% 
  filter(type == "TV", scored_by > 50000) %>% 
  mutate(premiered = as_factor(premiered),
         rating = as_factor(rating)) %>% 
  group_by(title_english) %>% 
  summarize(score = mean(score)) %>% 
  arrange(desc(score)) %>% 
  head(10)
```

