---
date: "8/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r}
pacman::p_load(dplyr, purrr, tidyr, ggplot2, ggtext, hrbrthemes, extrafont, 
               ggalt, ggforce, scales, ggrepel, forcats, ggupset,
               ggthemes, dutchmasters, ochRe, cowplot)

loadfonts(quiet = TRUE, device = "pdf")
```



  rise and fall of roman emperors
  
  
  gantt chart <>  ?
  bump chart
  beeswarm plot
  ggupset >>> rise - fall pairs
  
  ggtext color text
  
  x-axis year?
  facet_lump the "other" categories
  
  theme_solarized + greys

# Raw

```{r}
emperors_raw <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-13/emperors.csv")

glimpse(emperors_raw)
```


```{r}
emperors_raw %>% count(rise, sort = TRUE)
```



```{r}
emperors_raw %>% count(cause, sort = TRUE)
```

```{r}
  # mutate(dynasty = replace(dynasty, dynasty == "Julio-Claudian", 
  #                          "Julio-Claudian (27 B.C. - 68 A.D.)"),
  #        dynasty = replace(dynasty, dynasty == "Flavian", 
  #                          "Flavian (68 - 96 A.D.)"),
  #        dynasty = replace(dynasty, dynasty == "Nerva-Antonine", 
  #                          "Nerva-Antonine (96 - 192 A.D.)"),
  #        dynasty = replace(dynasty, dynasty == "Severan", 
  #                          "Severan (193 - 235 A.D.)"),
  #        dynasty = replace(dynasty, dynasty == "Julio-Claudian", 
  #                          "Julio-Claudian (27 B.C. - 68 A.D.)"))
```

# Clean

```{r}
emperors_clean <- emperors_raw %>% 
  select(-verif_who) %>% 
  mutate(rise = fct_relevel(rise, 
                            "Seized Power", "Appointment by Army",
                            "Appointment by Praetorian Guard",
                            "Purchase", "Election", 
                            "Appointment by Senate", 
                            "Appointment by Emperor",
                            "Birthright"),
         cause = fct_relevel(cause, 
                             "Assassination", "Unknown", "Execution", 
                             "Died in Battle", "Captivity", "Suicide", "Natural Causes"),
         dynasty = case_when(
           name %in% c("Trajan Decius", "Hostilian", 
                       "Trebonianus Gallus", "Aemilian") ~ "Decian",
           name %in% c("Valerian", "Gallienus") ~ "Valerian",
           name %in% c("Cladius Gothicus", "Quintillus", 
                       "Aurelian") ~ "Gordian cont.",
           name %in% c("Tacitus", "Florianus", "Probus") ~ "Tacitus",
           name %in% c("Carus", "Numerian", "Carinus") ~ "Caran",
           TRUE ~ dynasty)) %>% 
  mutate(dynasty = case_when(
    dynasty == "Julio-Claudian" ~ "Julio-Claudian (27 B.C. - 68 A.D.)",
    dynasty == "Flavian" ~ "Flavian (68 - 96 A.D.)",
    dynasty == "Nerva-Antonine" ~ "Nerva-Antonine (96 - 192 A.D.)",
    dynasty == "Severan" ~ "Severan (193 - 235 A.D.)",
    dynasty == "Gordian" ~ "Gordian (238 - 249 A.D.)",
    dynasty == "Gordian cont." ~ "Gordian cont. (268 - 275 A.D.)",
    dynasty == "Decian" ~ "Decian (249 - 253 A.D.)", 
    dynasty == "Valerian" ~ "Valerian (253 - 268 A.D.)",
    dynasty == "Tacitus" ~ "Tacitus (275 - 282 A.D.)", 
    dynasty == "Caran" ~ "Caran (282 - 285 A.D.)",
    dynasty == "Constantinian" ~ "Diocletian (285 - 305 A.D.)"
  )) %>% 
  mutate(dynasty = as_factor(dynasty))
```

green for peaceful, red for violent

ochRe::emu_woman_paired

ggsci::default_igv

dutchmasters::milkmaid

"#657b83"

# Plots

## Rise

```{r, fig.width=15}
emperors_rise <- emperors_clean %>% 
  filter(index <= 49) %>% 
  ggplot(aes(x = index, y = rise, group = 1)) +
  geom_path(color = "#657b83") +
  geom_point(aes(fill = dynasty), color = "grey",
             size = 5.5, shape = 21, stroke = 2) + 
  scale_x_continuous(expand = c(0.025, 0),
                   breaks = c(1, 49),
                   labels = c("26 B.C.", "305 A.D.")) +
  scale_fill_dutchmasters(palette = "pearl_earring") +
  guides(fill = guide_legend(title = "Dynasty", ncol = 3, 
                             direction = "horizontal", 
                             title.position = "top")) +
  labs(title = "The <b style='color: black'>Rise</b> & <b style='color: black'>Fall</b> of Roman Emperors <br>From Augustus (26 B.C. - 14 A.D.) to Diocletian (285 A.D. - 305 A.D.) <br>Transitions of Power Ordered by <b style='color:#228B22'>'Peaceful'</b> to <b style='color:#800000'>'Violent'</b> *",
       subtitle = "<b style='color: black'>Rise</b>",
       x = "26 B.C. - 395 A.D.", y = NULL,
       caption = glue::glue("
                            * Subjective and with many caveats
                            Data: Wikipedia
                            By @R_by_Ryo")) +
  theme_solarized() +
  theme(plot.title = element_markdown(size = 25, family = "Quattrocento"),
        plot.subtitle = element_markdown(size = 22, family = "Quattrocento"),
        plot.caption = element_text(size = 14),
        text = element_markdown(family = "Quattrocento", face = "bold"), 
        axis.title.x = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_line(size = 1.5),
        panel.grid.minor.x = element_blank(),
        axis.text.y = element_text(size = 16),
        legend.title = element_text(size = 18, family = "Quattrocento", face = "bold"),
        legend.text = element_text(size = 16, family = "Quattrocento", face = "bold"),
        legend.key = element_rect(fill = "#fdf6e3"),
        legend.position = "bottom")

emperors_rise
```


### tog version

```{r, fig.width=15}
windowsFonts(quattro = windowsFont("Quattrocento"))

emperors_riset <- emperors_clean %>% 
  filter(index <= 49) %>% 
  ggplot(aes(x = index, y = rise, group = 1)) +
  geom_path(color = "#657b83") +
  geom_point(aes(fill = dynasty), color = "grey",
             size = 5.5, shape = 21, stroke = 2) + 
  scale_x_discrete(expand = c(0.025, 0)) +
  scale_fill_dutchmasters(palette = "pearl_earring") +
  labs(title = "<b style='color: black'>Rise</b> of Roman Emperors",
       subtitle = "From Augustus (26 B.C. - 14 A.D.) to Diocletian (285 A.D. - 305 A.D.)  
       Transitions of Power Ordered by <b style='color:#228B22'>'Peaceful'</b> to <b style='color:#800000'>'Violent'</b> *",
       x = NULL, y = NULL) +
  theme_solarized() +
  theme(plot.title = element_markdown(size = 25, family = "quattro"),
        plot.subtitle = element_markdown(size = 20, family = "quattro"),
        text = element_markdown(family = "quattro", face = "bold"), 
        axis.title.x = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_line(size = 1.5),
        axis.text.y = element_text(size = 16),
        legend.position = "none",
        plot.margin = unit(c(9, 9, 9, 9), "pt"))

emperors_riset
```

```{r, fig.width=18}
windowsFonts(quattro = windowsFont("Quattrocento"))

emperors_riset2 <- emperors_clean %>% 
  filter(index <= 49) %>% 
  ggplot(aes(x = index, y = rise, group = 1)) +
  geom_path(color = "#657b83") +
  geom_point(aes(fill = dynasty), color = "grey",
             size = 5.5, shape = 21, stroke = 2) + 
  scale_x_continuous(expand = c(0.025, 0),
                   breaks = c(1, 49),
                   labels = c("26 B.C.", "305 A.D.")) +
  scale_fill_dutchmasters(palette = "pearl_earring") +
  labs(title = "The <b style='color: black'>Rise</b> & <b style='color: black'>Fall</b> of Roman Emperors <br>From Augustus (26 B.C. - 14 A.D.) to Diocletian (285 A.D. - 305 A.D.) <br>Transitions of Power Ordered by <b style='color:#228B22'>'Peaceful'</b> to <b style='color:#800000'>'Violent'</b> *",
       subtitle = "<b style='color: black'>Rise</b>",
       x = NULL, y = NULL) +
  theme_solarized() +
  theme(plot.title = element_markdown(size = 22, family = "quattro"),
        plot.subtitle = element_markdown(size = 22, family = "quattro"),
        plot.caption = element_text(size = 14),
        text = element_markdown(family = "quattro", face = "bold"), 
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_line(size = 1.5),
        panel.grid.minor.x = element_blank(),
        axis.text.y = element_text(size = 16),
        legend.title = element_text(size = 18, family = "quattro", face = "bold"),
        legend.text = element_text(size = 16, family = "quattro", face = "bold"),
        legend.key = element_rect(fill = "#fdf6e3"),
        legend.position = "none",
        plot.margin = unit(c(20, 20, 20, 20), "pt"))

emperors_riset2
```


## Fall

```{r, fig.width=15}
emperors_fall <- emperors_clean %>% 
  filter(index <= 49) %>% 
  ggplot(aes(x = index, y = cause, group = 1)) +
  geom_path(color = "#657b83") +
  geom_point(aes(fill = dynasty), color = "grey",
             size = 5.5, shape = 21, stroke = 2) + 
  scale_x_continuous(expand = c(0.025, 0),
                   breaks = c(1, 49),
                   labels = c("26 B.C.", "305 A.D.")) +
  scale_fill_dutchmasters(palette = "pearl_earring") +
  guides(fill = guide_legend(title = "Dynasty", ncol = 3, 
                             direction = "horizontal", 
                             title.position = "top")) +
  labs(title = "<b style='color: black'>Fall</b> of Roman Emperors",
       subtitle = "From Augustus (26 B.C. - 14 A.D.) to Diocletian (379 A.D. - 395 A.D.)  
       Transitions of Power Ordered by <b style='color:#228B22'>'Peaceful'</b> to <b style='color:#800000'>'Violent'</b> *",
       x = "Time: 26 B.C. - 305 A.D.", y = NULL,
       caption = glue::glue("* Subjective and with many caveats")) +
  theme_solarized() +
  theme(plot.title = element_markdown(size = 25, family = "Quattrocento"),
        plot.subtitle = element_markdown(size = 20, family = "Quattrocento"),
        plot.caption = element_text(size = 14),
        text = element_markdown(family = "Quattrocento", face = "bold"), 
        axis.title.x = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        #axis.ticks = element_blank(),
        panel.grid = element_line(size = 1.5),
        axis.text.y = element_text(size = 16),
        legend.title = element_text(size = 18, family = "Quattrocento", face = "bold"),
        legend.text = element_text(size = 16, family = "Quattrocento", face = "bold"),
        legend.key = element_rect(fill = "#fdf6e3"),
        legend.position = "bottom",
        legend.justification = c(0, 0))

emperors_fall
```



### tog version


```{r, fig.width=15}
windowsFonts(quattro = windowsFont("Quattrocento"))

emperors_fallt <- emperors_clean %>% 
  filter(index <= 49) %>% 
  ggplot(aes(x = index, y = cause, group = 1)) +
  geom_path(color = "#657b83") +
  geom_point(aes(fill = dynasty), color = "grey",
             size = 5.5, shape = 21, stroke = 2) + 
  scale_x_discrete(expand = c(0.025, 0)) +
  scale_fill_dutchmasters(palette = "pearl_earring") +
  guides(fill = guide_legend(title = "Dynasty", ncol = 3, 
                             direction = "horizontal", 
                             title.position = "top")) +
  labs(title = "<b style='color: black'>Fall</b> of Roman Emperors",
       x = "26 B.C. - 305 A.D.", y = NULL,
       caption = glue::glue("
                            * Subjective and with many caveats
                            Data: Wikipedia
                            By @R_by_Ryo")) +
  theme_solarized() +
  theme(plot.title = element_markdown(size = 25, family = "quattro"),
        plot.caption = element_text(size = 14),
        text = element_markdown(family = "quattro", face = "bold"), 
        axis.title.x = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_line(size = 1.5),
        axis.text.y = element_text(size = 16),
        legend.title = element_text(size = 18, family = "quattro", 
                                    face = "bold"),
        legend.text = element_text(size = 16, family = "quattro", 
                                   face = "bold"),
        legend.key = element_rect(fill = "#fdf6e3"),
        legend.position = "bottom",
        legend.justification = c(0, 0))

emperors_fallt
```



```{r, fig.width=18}
windowsFonts(quattro = windowsFont("Quattrocento"))

emperors_fallt2 <- emperors_clean %>% 
  filter(index <= 49) %>% 
  ggplot(aes(x = index, y = cause, group = 1)) +
  geom_path(color = "#657b83") +
  geom_point(aes(fill = dynasty), color = "grey",
             size = 5.5, shape = 21, stroke = 2) + 
  scale_x_continuous(expand = c(0.025, 0),
                   breaks = c(1, 49),
                   labels = c("26 B.C.", "305 A.D.")) +
  scale_fill_dutchmasters(palette = "pearl_earring") +
  guides(fill = guide_legend(title = "Dynasty", ncol = 3, 
                             direction = "horizontal", 
                             title.position = "top")) +
  labs(title = NULL,
       subtitle = "<b style='color: black'>Fall</b>",
       x = "The Principate Era", y = NULL,
       caption = glue::glue("
                            * Subjective and with many caveats
                            Data: Wikipedia
                            By @R_by_Ryo")) +
  theme_solarized() +
  theme(plot.subtitle = element_markdown(size = 22, family = "quattro"),
        plot.caption = element_text(size = 14),
        text = element_markdown(family = "quattro", face = "bold"), 
        axis.title.x = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.ticks = element_blank(),
        panel.grid = element_line(size = 1.5),
        panel.grid.minor.x = element_blank(),
        axis.text.y = element_text(size = 16),
        legend.title = element_text(size = 18, family = "quattro", face = "bold"),
        legend.text = element_text(size = 16, family = "quattro", face = "bold"),
        legend.key = element_rect(fill = "#fdf6e3"),
        legend.position = "bottom",
        legend.justification = c(0, 0),
        plot.margin = unit(c(20, 20, 20, 20), "pt"))

emperors_fallt2
```



# Together


```{r, fig.height=20, fig.width=15}
library(gtable)
library(grid)

png("emperor_RiseFall_plot.png", 
    width = 2000, height = 1500, res = 144, bg = "white")

one <- ggplotGrob(emperors_riset)
two <- ggplotGrob(emperors_fallt)

gg <- rbind(one, two, size = "last")
gg

gg$widths <- unit.pmax(one$widths, two$widths)

#gg$layout[grepl("guide", gg$layout$name), c("t", "b")] <- c(1, nrow(gg))

grid.newpage()
grid.draw(gg)

dev.off()
```

```{r, fig.height=20, fig.width=18}
library(gtable)
library(grid)

png("emperor_RiseFall_plot2.png", 
    width = 2000, height = 1800, res = 144, bg = "white")

one <- ggplotGrob(emperors_riset2)
two <- ggplotGrob(emperors_fallt2)

gg <- rbind(one, two, size = "last")
gg

gg$widths <- unit.pmax(one$widths, two$widths)

grid.newpage()
grid.draw(gg)

dev.off()
```









## misc.


```{r, fig.height=20, fig.width=15, warning=FALSE, message=FALSE}
asdf <- plot_grid(emperors_riset, emperors_fallt, 
          align = "v", #axis = "l",
          ncol = 1)

set_null_device("pdf")

ggdraw(asdf)
```


```{r}
ggsave(filename = here::here("roman_emperors_plot.png"),
       height = 20, width = 15)
```




```{r}
library(gridExtra)

png("test_plot.png", 
    width = 2000, height = 1500, res = 144, bg = "white")

grid.arrange(
  emperors_riset, 
  emperors_fallt, widths = c(1)
  )
dev.off()
```





```{r}
asdf

Cairo::Cairo(2000, 1500, "test.png", bg = "white")
last_plot()
dev.off()
```


```{r, fig.height=20, fig.width=15}
library(gtable)
library(grid)

one <- ggplotGrob(emperors_riset)
two <- ggplotGrob(emperors_fallt)

panel_id <- one$layout[one$layout$name == "panel", c("t", "l")]

g <- gtable_add_rows(one, unit(1, "in"), 0)
g <- gtable_add_grob(g, two,
                     t = 1, l = panel_id$l)

grid.newpage()
grid.draw(g)
```








```{r, fig.height=20, fig.width=15}
ggpubr::ggarrange(emperors_riset, 
                  emperors_fallt, 
                  ncol = 1, align = "v")
```





```{r}
library(gridExtra)
justify <- function(x, hjust="center", vjust="center", draw=TRUE){
  w <- sum(x$widths)
  h <- sum(x$heights)
  xj <- switch(hjust,
               center = 0.5,
               left = 0.5*w,
               right=unit(1,"npc") - 0.5*w)
  yj <- switch(vjust,
               center = 0.5,
               bottom = 0.5*h,
               top=unit(1,"npc") - 0.5*h)
  x$vp <- grid::viewport(x=xj, y=yj)
  if(draw) grid::grid.draw(x)
  return(x)
}

grid::grid.newpage()
justify(emperors_riset,
        emperors_fallt, "left", "top")
```




# Upset plots






```{r, fig.height=5, fig.width=8}
emperors_clean %>% 
  mutate_at(c("rise", "cause"), as.character) %>% 
  mutate(rise = paste0("<b style='color: black'>Rise</b>: ", rise),
         cause = paste0("<b style='color: black'>Fall</b>: ", cause)) %>% 
  mutate(risefall = map2(rise, cause, ~c(.x, .y))) %>% 
  ggplot(aes(x = risefall)) +
  geom_bar(fill = "#8B0000") + 
  scale_x_upset(n_intersections = 10,
                expand = c(0.01, 0.01)) +
  scale_y_continuous(expand = c(0, 0),
                     labels = seq(0, 15, by = 2),
                     breaks = seq(0, 15, by = 2)) +
  labs(title = "The <b style='color: black'>Rise</b> & <b style='color: black'>Fall</b> of Roman Emperors",
       subtitle = "Many Emperors With A 'Rightful' Claim Met An <br> Untimely End By <b style='color: #8B0000'>Assassination</b> Or <b style='color: #8B0000'>Execution</b>.",
       caption = "<b style='color: black'>Source</b>: Wikipedia <br><b style='color: black'>By</b>: @R_by_Ryo",
       x = NULL, y = "Number of Occurence") +
  theme_combmatrix(
    text = element_text(family = "Quattrocento", color = "#657b83"),
    plot.title = element_markdown(family = "Quattrocento"),
    plot.subtitle = element_markdown(family = "Quattrocento"),
    plot.caption = element_markdown(family = "Quattrocento"),
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(family = "Quattrocento", color = "#657b83", size = 10),
    plot.background = element_rect(fill = "#fdf6e3"),
    panel.background = element_rect(fill = "#fdf6e3"),
    combmatrix.panel.striped_background.color.one = "#d3d3d3",
    combmatrix.panel.point.color.fill = "#8B0000",
    combmatrix.panel.line.color = "#8B0000",   ## added this option in myself in my own version of the package...
    panel.grid.major.x = element_blank(),
    combmatrix.label.extra_spacing = 5,
    axis.ticks = element_blank())
```

```{r}
ggsave(filename = here::here("emperors_upsetplot.png"),
       height = 5, width = 8)
```












